Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2018-12-19 Manuscript/manuscript.Rmd
Merge ensemble comparison methods to the results

Using set notation the formulation of the ensemble framework can be defined as follows:

Set of different resolutions:

R = {5kb, 25kb, 50kb, 100kb}

Set of Predictor Types:

P = {OC, OP, Distance}

Set of Variable Reduction Techniques:

V = {LASSO, Elastic-Net}

Set of Class-Balancing Methods:

C = {None, RUS, ROS, SMOTE}

Therefore, a system produced from the ensemble framework is defined as follows:

E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.

Once a system was defined, a random forest algorithm was performed. Letting |X| denote the cardinality of each set, then we evaluated |R| x |P| x |V| x |C| different ensemble systems.

@@

In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system. We evaluated and compared 4 domain data sets, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques. Thus, we generated 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models. For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.

>>>>

@@

We evaluated and compared Hi-C datasets at four different resolutions R = {5kb, 25kb, 50kb, 100kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and four class balancing techniques C = {None, RUS, ROS, SMOTE}. Therefore, a system produced from the ensemble framework is defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C. Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models. For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.
